Digital enhancement of the ``Paolo Orsi'' museum: a Google Street View 360° pilot project tour

### 2015-12-16 source/17/Zuddas Epigraphy in Italian High Schools (final).tex
other biblio added till paper 20

Highly original suggestions have been provided by Mauro Reali, who is also the author of different school manuals, in a
paper published online\footnote{\url{http://mediaclassica.loescher.it/nuove-e-\%93vecchie\%94-forme-di-multimedialita.n2799}
; see also \citep{Reali2015}.}. Being an expert on the subject, he offers a comparison between the ``noble'' form of
the political-philosophical amicitia presented in Cicero’s Laelius and the term \emph{amicus} mentioned in inscriptions
from the lower levels of society, such as CIL 05, 05300 from \emph{Comum} (a funerary stela made by a freedman for
Pliny the Younger) or CIL 05, 05923 = EDR124245 regarding a strange case of ``friend deletion'' long before the Facebook
era\footnote{ \url{http://www.laricerca.loescher.it/lingue-classiche/327-un-amico-o-amicus-e-per-sempre.html}.}.

@@

\begin{quotation}
[{}- - - I]o[323?]vino consulibb(us) (ante diem) VIII Kal(endas) Martias domum oscilavi Musae. 
\end{quotation}

>>>>

Highly original suggestions have been provided by Mauro Reali, who is also the author of different school manuals, in a
paper published online\footnote{\url{http://mediaclassica.loescher.it/nuove-e-\%93vecchie\%94-forme-di-multimedialita.n2799}
; see also \citet{Reali2015}.}. Being an expert on the subject, he offers a comparison between the ``noble'' form of
the political-philosophical amicitia presented in Cicero’s Laelius and the term \emph{amicus} mentioned in inscriptions
from the lower levels of society, such as CIL 05, 05300 from \emph{Comum} (a funerary stela made by a freedman for
Pliny the Younger) or CIL 05, 05923 = EDR124245 regarding a strange case of ``friend deletion'' long before the Facebook
era\footnote{ \url{http://www.laricerca.loescher.it/lingue-classiche/327-un-amico-o-amicus-e-per-sempre.html}.}.

@@

\begin{quotation}

[{}- - - I]ọvino consulibb(us) (ante diem) VIII Kal(endas) Martias domum oscilavi Musae. 
\end{quotation}

### 2015-12-16 source/20/EAGLE2016_BONACINI - Pilot project at Paolo Orsi Museum.tex
other biblio added till paper 20

\title{Digital enhancement of the ``Paolo Orsi'' museum: a Google Street View 360° pilot project tour}
\author[catania]{Elisa Bonacini\corref{first}}
\cortext[first]{Corresponding author. Email: e_bonacini@hotmail.com; elisa.bonacini@unict.it}

\address[catania]{Humanities Department, University of Catania; IEMEST (Istituto Euro Mediterraneo di Scienze e Tecnologie), Palermo, Italy}
\date{2015-12-11}
\begin{document}

@@

Despite of this, Sicilian cultural heritage struggles to be present on Google’s platforms such as Google Art Project and
others, as it should, compared to other Italian cultural sites \citep{Bonacini2013;Bonacini2014}).

@@

The inscription says: ``Oh friend, you see here the tomb of Nassiane, Christian, ripe, sweet, fond of her husband, who
competed for virtue with Penelope. Here lies Nassiane, she lived well and blamelessly in God (?), 32 years and 10
months''. This inscription documents such as epigraphic formulas affected by religious syncretism (syncretism generally
means that a complex of phenomena and concepts derive from the meeting and fusion of different religious forms) between
Pagans and Christians, for which a Christian like Nassiane could have competed in life with Penelope, the hero
Odysseus’ wife and symbol of marital devotion. Its circular shape suggested that it was a table for the ritual of
refrigerium, the funeral feast that symbolically was consumed with the dead, even this syncretic practice \ dates back
to the pagan world \citep{Sgarlata2013;Scandurra2014}.

>>>>

\title{Digital enhancement of the ``Paolo Orsi'' museum: a Google Street View 360° pilot project tour}
\author[catania]{Elisa Bonacini\corref{first}}
\cortext[first]{Corresponding author. Email: e_bonacini@hotmail.com; elisa.bonacini@unict.it}
\address[catania]{Humanities Department, University of Catania; IEMEST (Istituto Euro Mediterraneo di Scienze e Tecnologie), Palermo, Italy}
\date{2015-12-11}
\begin{document}

@@

Despite of this, Sicilian cultural heritage struggles to be present on Google’s platforms such as Google Art Project and
others, as it should, compared to other Italian cultural sites \citep{Bonacini2013} \citep{Bonacini2014}).

@@

The inscription says: ``Oh friend, you see here the tomb of Nassiane, Christian, ripe, sweet, fond of her husband, who
competed for virtue with Penelope. Here lies Nassiane, she lived well and blamelessly in God (?), 32 years and 10
months''. This inscription documents such as epigraphic formulas affected by religious syncretism (syncretism generally
means that a complex of phenomena and concepts derive from the meeting and fusion of different religious forms) between
Pagans and Christians, for which a Christian like Nassiane could have competed in life with Penelope, the hero
Odysseus’ wife and symbol of marital devotion. Its circular shape suggested that it was a table for the ritual of
refrigerium, the funeral feast that symbolically was consumed with the dead, even this syncretic practice \ dates back
to the pagan world \citep{Sgarlata2013}, \citep{Scandurra2014}.
